\vspace{-2.7cm}A generative model for urban firm networks

### 2019-11-15 extended_abstract.tex
Update on Overleaf.
.

\title{\vspace{-2.5cm}A generative model for urban firm networks}
\author{J. Raimbault$^{1,2,3}$, N. Zdanowska$^{1,3}$ and E. Arcaute$^1$\\\medskip\small
$^{1}$ Centre for Advanced Spatial Analysis, UCL; $^{2}$ UPS CNRS 3611 ISC-PIF; $^{3}$ UMR CNRS 8504 G{\'e}ographie-cit{\'e}s
}
\date{}

@@

%\begin{abstract}
%    We introduce a generative network model for urban networks of interactions between firms. The growth of the network is simulated by adding new firm ownership links randomly, with probabilities determined by several factors, namely the economic size of origin and destination urban areas, industrial sector proximity, the strength of previous links, and geographical and socio-cultural distance. Simulation on synthetic systems of cities unveil phase transitions when changing interaction distance, and non-trivial patterns in model behavior. Future work include the calibration of the model on real company links for Europe.
%\end{abstract}

@@

We show in Fig. 1 examples of generated networks, with very contrasted patterns obtained with different spatial interaction ranges. This behavior is confirmed when plotting the internationalization index against the distance, which shows an exponential decay. Similarly, the correlation between city weighted degree and city size exhibit a behaviour that can be interpreted as a phase transition between local and global networks. Other indicators exhibit non-trivial patterns. For example, when considering average community size of the final network, we obtain a maximal integration in term of communities at an intermediate value of the gravity decay, what can be interpreted as the emergence of a regional regime. The size of communities is largely influenced by the value of the elasticities for the similarity function and the ratio of the economic output of the area. Altogether, these experiments reveal a complex interplay between processes and how the model produces diverse stylized facts.

>>>>

\title{\vspace{-2.7cm}A generative model for urban firm networks}
\author{J. Raimbault$^{1,2,3}$, N. Zdanowska$^{1,3}$ and E. Arcaute$^1$\\\medskip\small
$^{1}$ Centre for Advanced Spatial Analysis, UCL; $^{2}$ UPS CNRS 3611 ISC-PIF; $^{3}$ UMR CNRS 8504 G{\'e}ographie-cit{\'e}s
}
\date{}

@@

%\begin{abstract}
%    We introduce a generative network model for urban networks of interactions between firms. The growth of the network is simulated by adding new firm ownership links randomly, with probabilities determined by several factors, namely the economic size of origin and destination urban areas, industrial sector proximity, the strength of previous links, and geographical and socio-cultural distance. Simulation on synthetic systems of cities unveil phase transitions when changing interaction distance, and non-trivial patterns in model behavior. We also give first results of  calibrating the model on real company links for Europe using a genetic algorithm.
%\end{abstract}

% Keywords
% Urban Firm Networks
% Generative Network Model
% Model Exploration

@@

We show in Fig. 1 examples of generated networks, with very contrasted patterns obtained with different spatial interaction ranges. This behavior is confirmed when plotting the internationalization index against the distance, which shows an exponential decay. Similarly, the correlation between city weighted degree and city size exhibit a behaviour that can be interpreted as a phase transition between local and global networks. Other indicators exhibit non-trivial patterns. For example, when considering average community size of the final network, we obtain a maximal integration in term of communities at an intermediate value of the gravity decay, what can be interpreted as the emergence of a regional regime. The size of communities is largely influenced by the value of the elasticities for the similarity function and the ratio of the economic output of the area. All these experiments reveal a complex interplay between processes and how the model produces diverse stylized facts.
